---
title: "Analysis Draft"
output: html_document
date: "2022-11-22"
---

##Overview:
Hypothesis 1: The mean well being score of participants will be significantly higher in the group that underwent mindfulness training

Hypothesis 2: There will be a positive correlation with a high R squared when comparing well being and competency ratings

Hypothesis 3: There will be a significant increase in the mean well being of individuals with high emotional intelligence scores

We will be using a one-tailed t-test for our first hypothesis, a correlational analysis for our second hypothesis, and a two factor ANOVA for our third hypothesis. Link to preregistration with more information about data and analyses (https://doi.org/10.17605/OSF.IO/SJWM9)


```{r libraries, include=FALSE}
library(ggplot2)
library(tidyverse)
library(car)
```


##Data Set-up
```{r}
setwd("C:/Users/kaile/OneDrive/Desktop/R Projects/Secondary-Analysis-of-the-implementation-of-Online-Mindfulness-Training-on-Well-Being-Trait-Emotion")

MindfulnessDat<- read.csv("C:/Users/kaile/Downloads/MindfulnessData_fullunmatched_raw_items_NadlerCarswellMinda (1).csv", dec=",")

NadlerDat<- read.csv("C:/Users/kaile/Downloads/MindfulnessDataExport_NadlerCarswellMinda2020.csv", header=TRUE, dec=",")

```

##Data Cleaning

###Mindfulness Data
```{r}
MindfulnessDat$grouping <- NA

for(i in 1:nrow(MindfulnessDat)){
  if(MindfulnessDat$Group[i]=="Participant"){
    MindfulnessDat$grouping[i] <- 2
  }
  else{
    MindfulnessDat$grouping[i] <- 1
  }
}

MindfulnessDat$grouping <- as.numeric(MindfulnessDat$grouping)
MindfulnessDatParticipant <- MindfulnessDat %>% filter(grouping=="2")
```

###Wellbeing Data
```{r}
MindfulnessDatParticipant$FacetQuestMean <- NA

for(i in 1:nrow(MindfulnessDatParticipant)) {
  MindfulnessDatParticipant$FacetQuestMean[i] <- ((MindfulnessDatParticipant$X5.facet.questionnaire.short.form[i]
                                         +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.1[i]
                                         +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.2[i]
                                         +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.3[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.4[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.5[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.6[i]
                                         +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.7[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.8[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.9[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.10[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.11[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.12[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.13[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.14[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.15[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.16[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.17[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.18[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.19[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.20[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.21[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.22[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.23[i])/24)
}
```

##Wellbeing Data Hypothesis 3
```{r}
MindfulnessDat$FacetQuestMean <- NA
for(i in 1:nrow(MindfulnessDat)) {
  MindfulnessDat$FacetQuestMean[i] <- ((MindfulnessDat$X5.facet.questionnaire.short.form[i]
                                         +MindfulnessDat$X5.facet.questionnaire.short.form.1[i]
                                         +MindfulnessDat$X5.facet.questionnaire.short.form.2[i]
                                         +MindfulnessDat$X5.facet.questionnaire.short.form.3[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.4[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.5[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.6[i]
                                         +MindfulnessDat$X5.facet.questionnaire.short.form.7[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.8[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.9[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.10[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.11[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.12[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.13[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.14[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.15[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.16[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.17[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.18[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.19[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.20[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.21[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.22[i]
                                        +MindfulnessDat$X5.facet.questionnaire.short.form.23[i])/24)
}
```

###Competency Data
```{r}
MindfulnessDatParticipant$Competency <- NA

for(i in 1:nrow(MindfulnessDatParticipant)){
  MindfulnessDatParticipant$Competency[i] <- ((MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.1[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.2[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.3[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.4[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.5[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.6[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.7[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.8[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.9[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.10[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.11[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.12[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.13[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.14[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.15[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.16[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.17[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.18[i] +MindfulnessDatParticipant$Positive.and.Negative.Affect.Schedule.19[i])/20)}

MindfulnessDatParticipant$Competency2 <- NA

for(i in 1:nrow(MindfulnessDatParticipant)){  
  MindfulnessDatParticipant$Competency2[i] <- ((MindfulnessDatParticipant$Brief.Resilience.Scale[i] +MindfulnessDatParticipant$Brief.Resilience.Scale.1[i] +MindfulnessDatParticipant$Brief.Resilience.Scale.2[i]                                +MindfulnessDatParticipant$Brief.Resilience.Scale.3[i] +MindfulnessDatParticipant$Brief.Resilience.Scale.4[i] +MindfulnessDatParticipant$Brief.Resilience.Scale.5[i])/6)}
```

###Emotional Intelligence Data
```{r}
MindfulnessDat$MeanMEIAWeek <- NA

for(i in 1:nrow(MindfulnessDat)){
  MindfulnessDat$MeanMEIAWeek[i] <- ((MindfulnessDat$MEIA.W[i]
                                      +MindfulnessDat$MEIA.W.1[i]
                                      +MindfulnessDat$MEIA.W.2[i]
                                      +MindfulnessDat$MEIA.W.3[i]
                                      +MindfulnessDat$MEIA.W.4[i]
                                      +MindfulnessDat$MEIA.W.5[i]
                                      +MindfulnessDat$MEIA.W.6[i]
                                      +MindfulnessDat$MEIA.W.7[i]
                                      +MindfulnessDat$MEIA.W.8[i]
                                      +MindfulnessDat$MEIA.W.9[i]
                                      +MindfulnessDat$MEIA.W.10[i]
                                      +MindfulnessDat$MEIA.W.11[i]
                                      +MindfulnessDat$MEIA.W.12[i]
                                      +MindfulnessDat$MEIA.W.13[i]
                                      +MindfulnessDat$MEIA.W.14[i]
                                      +MindfulnessDat$MEIA.W.15[i]
                                      +MindfulnessDat$MEIA.W.16[i]
                                      +MindfulnessDat$MEIA.W.17[i]
                                      +MindfulnessDat$MEIA.W.18[i]
                                      +MindfulnessDat$MEIA.W.19[i]
                                      +MindfulnessDat$MEIA.W.20[i]
                                      +MindfulnessDat$MEIA.W.21[i]
                                      +MindfulnessDat$MEIA.W.22[i]
                                      +MindfulnessDat$MEIA.W.23[i]
                                      +MindfulnessDat$MEIA.W.24[i]
                                      +MindfulnessDat$MEIA.W.25[i]
                                      +MindfulnessDat$MEIA.W.26[i]
                                      +MindfulnessDat$MEIA.W.27[i]
                                      +MindfulnessDat$MEIA.W.28[i]
                                      +MindfulnessDat$MEIA.W.29[i]
                                      +MindfulnessDat$MEIA.W.30[i]
                                      +MindfulnessDat$MEIA.W.31[i]
                                      +MindfulnessDat$MEIA.W.32[i]
                                      +MindfulnessDat$MEIA.W.33[i]
                                      +MindfulnessDat$MEIA.W.34[i]
                                      +MindfulnessDat$MEIA.W.35[i]
                                      +MindfulnessDat$MEIA.W.36[i]
                                      +MindfulnessDat$MEIA.W.37[i]
                                      +MindfulnessDat$MEIA.W.38[i]
                                      +MindfulnessDat$MEIA.W.39[i]
                                      +MindfulnessDat$MEIA.W.40[i]
                                      +MindfulnessDat$MEIA.W.41[i]
                                      +MindfulnessDat$MEIA.W.42[i]
                                      +MindfulnessDat$MEIA.W.43[i]
                                      +MindfulnessDat$MEIA.W.44[i]
                                      +MindfulnessDat$MEIA.W.45[i]
                                      +MindfulnessDat$MEIA.W.46[i]
                                      +MindfulnessDat$MEIA.W.47[i]
                                      +MindfulnessDat$MEIA.W.48[i]
                                      +MindfulnessDat$MEIA.W.49[i]
                                      +MindfulnessDat$MEIA.W.50[i]
                                      +MindfulnessDat$MEIA.W.51[i]
                                      +MindfulnessDat$MEIA.W.52[i]
                                      +MindfulnessDat$MEIA.W.53[i]
                                      +MindfulnessDat$MEIA.W.54[i]
                                      +MindfulnessDat$MEIA.W.55[i]
                                      +MindfulnessDat$MEIA.W.56[i]
                                      +MindfulnessDat$MEIA.W.57[i]
                                      +MindfulnessDat$MEIA.W.58[i]
                                      +MindfulnessDat$MEIA.W.59[i]
                                      +MindfulnessDat$MEIA.W.60[i]
                                      +MindfulnessDat$MEIA.W.61[i]
                                      +MindfulnessDat$MEIA.W.62[i]
                                      +MindfulnessDat$MEIA.W.63[i]
                                      +MindfulnessDat$MEIA.W.64[i]
                                      +MindfulnessDat$MEIA.W.65[i]
                                      +MindfulnessDat$MEIA.W.66[i]
                                      +MindfulnessDat$MEIA.W.67[i]
                                      +MindfulnessDat$MEIA.W.68[i]
                                      +MindfulnessDat$MEIA.W.69[i]
                                      +MindfulnessDat$MEIA.W.70[i]
                                      +MindfulnessDat$MEIA.W.71[i])/72)
}

```

###Emotional Intelligence Level Data
```{r}
MindfulnessDat$LevelMEIA <- NA

for(i in 1:nrow(MindfulnessDat)){
  if(MindfulnessDat$MeanMEIAWeek[i] > 3.56 || is.na(MindfulnessDat$MeanMEIAWeek)[i]== TRUE){
    MindfulnessDat$LevelMEIA[i] <- "high"
  }
  else{
    MindfulnessDat$LevelMEIA[i] <- "low"
  }
}
```


##Hypothesis 1 Analysis
###Paired samples t-test
```{r}
t.test(MindfulnessDatParticipant$FacetQuestMean ~ MindfulnessDatParticipant$Before.mindfulness.training.or.after, alternative = "greater", var.equal= TRUE, na.rm = TRUE)

```

```{r, include= FALSE}
sd1 <- sd(MindfulnessDatParticipant$FacetQuestMean, na.rm = TRUE)
```

```{r}
ggplot(MindfulnessDatParticipant, aes(Before.mindfulness.training.or.after, FacetQuestMean), na.rm = TRUE) + geom_bar(stat = 'identity', position = position_dodge(), fill = "darkblue") + ggtitle("Mindfulness before and after training") + xlab("") + ylab("Mindfulness") + geom_errorbar(aes(ymin= FacetQuestMean-sd1, ymax= FacetQuestMean + sd1)) 
```


##Hypothesis 2 Analysis

###Competency Correlation 1: A correlation was run on Mindfulness and Competency based on Positive or Negative Affect. We are also calculating variance through R^2.
```{r}
cor.test(MindfulnessDatParticipant$Competency, MindfulnessDatParticipant$FacetQuestMean)
comp1lm <- lm(Competency~FacetQuestMean, data = MindfulnessDatParticipant)
summary(comp1lm)
```

```{r}
ggplot(MindfulnessDatParticipant, aes(Competency, FacetQuestMean)) + geom_point() + geom_smooth(method = "lm") + xlab("Competency 1") + ylab("Wellbeing") 
```

###Competency Correlation 2: A correlation was run on Mindfulnes and Competency based on Resilience Scale. We are also calculating variance through R^2.
```{r}
cor.test(MindfulnessDatParticipant$Competency2, MindfulnessDatParticipant$FacetQuestMean)
comp2lm <- lm(Competency2~FacetQuestMean, data = MindfulnessDatParticipant)
summary(comp2lm)
```

```{r}
ggplot(MindfulnessDatParticipant, aes(Competency2, FacetQuestMean)) + geom_point() + geom_smooth(method = "lm") + xlab("Competency 2") + ylab("Wellbeing") 
```


##Hypothesis 3 Analysis
```{r}
mean(MindfulnessDat$MeanMEIAWeek, na.rm = TRUE)

lmH3<- lm(MindfulnessDat$FacetQuestMean ~ MindfulnessDat$LevelMEIA)
Anova(lmH3)
```
```{r}
ggplot(MindfulnessDat, aes(MeanMEIAWeek, FacetQuestMean, fill = LevelMEIA)) + geom_point(shape = 21)+ geom_smooth(method = "lm")+ xlab("Emotional Intelligence Mean Score")+ ylab("Well Being Mean Score")
```
