---
title: "Analysis Draft"
output: html_document
date: "2022-11-22"
---

##Overview:
Hypothesis 1: The mean well being score of participants will be significantly higher in the group that underwent mindfulness training

Hypothesis 2: There will be a positive correlation with a high R squared when comparing well being and competency ratings

Hypothesis 3: There will be a significant increase in the mean well being of individuals with high emotional intelligence scores

We will be using a one-tailed t-test for our first hypothesis, a correlational analysis for our second hypothesis, and a two factor ANOVA for our third hypothesis. Link to preregistration with more information about data and analyses (https://doi.org/10.17605/OSF.IO/SJWM9)


##Data Cleaning
```{r}
MindfulnessDat<- read.csv("C:/Users/kaile/Downloads/MindfulnessData_fullunmatched_raw_items_NadlerCarswellMinda.csv", header=TRUE)
NadlerDat<- read.csv("C:/Users/kaile/Downloads/MindfulnessDataExport_NadlerCarswellMinda2020.csv", header=TRUE, dec=",")


#Will be meeting with Dr. Woodward to clean multiple headings on datasets and address the weird column situation on MindfulnessDat.
```


##Hypothesis 1 Analysis
```{r}
library(ggplot2)
library(tidyverse)

MindfulnessDat$grouping <- NA

for(i in 1:nrow(MindfulnessDat)){
  if(MindfulnessDat$Group[i]=="Participant"){
    MindfulnessDat$grouping[i] <- 2
  }
  else{
    MindfulnessDat$grouping[i] <- 1
  }
}

summary(MindfulnessDat$grouping)
MindfulnessDat$grouping <- as.numeric(MindfulnessDat$grouping)
MindfulnessDatParticipant <- MindfulnessDat %>% filter(grouping=="2")

#FFMQ questionaire used to asses well being

MindfulnessDatParticipant$FacetQuestMean <- NA

for(i in 1:nrow(MindfulnessDatParticipant)){
  MindfulnessDatParticipant$FacetQuestMean[i] <- ((MindfulnessDatParticipant$X5.facet.questionnaire.short.form[i]
                                         +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.1[i]
                                         +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.2[i]
                                         +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.3[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.4[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.5[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.6[i]
                                         +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.7[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.8[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.9[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.10[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.11[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.12[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.13[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.14[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.15[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.16[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.17[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.18[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.19[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.20[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.21[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.22[i]
                                        +MindfulnessDatParticipant$X5.facet.questionnaire.short.form.23[i])/24)
}

t.test(MindfulnessDatParticipant$FacetQuestMean ~ MindfulnessDatParticipant$Before.mindfulness.training.or.after, alternative = "greater", na.rm = TRUE)

#Make a graph showing t test next
```

##Hypothesis 2 Analysis
```{r}
#running a correlational analysis between well being and competency ratings. First we need to clean up the data from above, but there is an issue with multiple headers and anchoring information on the MindfullnessDat data set that needs to be addressed with Dr. Woodward.

mean(MindfulnessDat$wellbeing)
mean(MindfulnessDat$competency)
cor.test(MindfulnessDat$wellbeing~ MindfulnessDat$competency)
library(ggplot2)
ggplot(MindfullnessDat, aes(wellbeing, competency)) + geom_point() + geom_smooth(method = "lm")

#R^2
cor("y actual", "y predict")^2

```


##Hypothesis 3 Analysis

```{r}
library(ggplot2)
library(tidyverse)
library(car)

#Emotional Intelligence Scores comes from MEIA questions
MindfulnessDat$MeanMEIAWeek <- NA
MindfulnessDat$LevelMEIA <- NA

for(i in 1:nrow(MindfulnessDat)){
  MindfulnessDat$MeanMEIAWeek[i] <- ((MindfulnessDat$MEIA.W[i]
                                      +MindfulnessDat$MEIA.W.1[i]
                                      +MindfulnessDat$MEIA.W.2[i]
                                      +MindfulnessDat$MEIA.W.3[i]
                                      +MindfulnessDat$MEIA.W.4[i]
                                      +MindfulnessDat$MEIA.W.5[i]
                                      +MindfulnessDat$MEIA.W.6[i]
                                      +MindfulnessDat$MEIA.W.7[i]
                                      +MindfulnessDat$MEIA.W.8[i]
                                      +MindfulnessDat$MEIA.W.9[i]
                                      +MindfulnessDat$MEIA.W.10[i]
                                      +MindfulnessDat$MEIA.W.11[i]
                                      +MindfulnessDat$MEIA.W.12[i]
                                      +MindfulnessDat$MEIA.W.13[i]
                                      +MindfulnessDat$MEIA.W.14[i]
                                      +MindfulnessDat$MEIA.W.15[i]
                                      +MindfulnessDat$MEIA.W.16[i]
                                      +MindfulnessDat$MEIA.W.17[i]
                                      +MindfulnessDat$MEIA.W.18[i]
                                      +MindfulnessDat$MEIA.W.19[i]
                                      +MindfulnessDat$MEIA.W.20[i]
                                      +MindfulnessDat$MEIA.W.21[i]
                                      +MindfulnessDat$MEIA.W.22[i]
                                      +MindfulnessDat$MEIA.W.23[i]
                                      +MindfulnessDat$MEIA.W.24[i]
                                      +MindfulnessDat$MEIA.W.25[i]
                                      +MindfulnessDat$MEIA.W.26[i]
                                      +MindfulnessDat$MEIA.W.27[i]
                                      +MindfulnessDat$MEIA.W.28[i]
                                      +MindfulnessDat$MEIA.W.29[i]
                                      +MindfulnessDat$MEIA.W.30[i]
                                      +MindfulnessDat$MEIA.W.31[i]
                                      +MindfulnessDat$MEIA.W.32[i]
                                      +MindfulnessDat$MEIA.W.33[i]
                                      +MindfulnessDat$MEIA.W.34[i]
                                      +MindfulnessDat$MEIA.W.35[i]
                                      +MindfulnessDat$MEIA.W.36[i]
                                      +MindfulnessDat$MEIA.W.37[i]
                                      +MindfulnessDat$MEIA.W.38[i]
                                      +MindfulnessDat$MEIA.W.39[i]
                                      +MindfulnessDat$MEIA.W.40[i]
                                      +MindfulnessDat$MEIA.W.41[i]
                                      +MindfulnessDat$MEIA.W.42[i]
                                      +MindfulnessDat$MEIA.W.43[i]
                                      +MindfulnessDat$MEIA.W.44[i]
                                      +MindfulnessDat$MEIA.W.45[i]
                                      +MindfulnessDat$MEIA.W.46[i]
                                      +MindfulnessDat$MEIA.W.47[i]
                                      +MindfulnessDat$MEIA.W.48[i]
                                      +MindfulnessDat$MEIA.W.49[i]
                                      +MindfulnessDat$MEIA.W.50[i]
                                      +MindfulnessDat$MEIA.W.51[i]
                                      +MindfulnessDat$MEIA.W.52[i]
                                      +MindfulnessDat$MEIA.W.53[i]
                                      +MindfulnessDat$MEIA.W.54[i]
                                      +MindfulnessDat$MEIA.W.55[i]
                                      +MindfulnessDat$MEIA.W.56[i]
                                      +MindfulnessDat$MEIA.W.57[i]
                                      +MindfulnessDat$MEIA.W.58[i]
                                      +MindfulnessDat$MEIA.W.59[i]
                                      +MindfulnessDat$MEIA.W.60[i]
                                      +MindfulnessDat$MEIA.W.61[i]
                                      +MindfulnessDat$MEIA.W.62[i]
                                      +MindfulnessDat$MEIA.W.63[i]
                                      +MindfulnessDat$MEIA.W.64[i]
                                      +MindfulnessDat$MEIA.W.65[i]
                                      +MindfulnessDat$MEIA.W.66[i]
                                      +MindfulnessDat$MEIA.W.67[i]
                                      +MindfulnessDat$MEIA.W.68[i]
                                      +MindfulnessDat$MEIA.W.69[i]
                                      +MindfulnessDat$MEIA.W.70[i]
                                      +MindfulnessDat$MEIA.W.71[i])/72)
}

mean(MindfulnessDat$MeanMEIAWeek, na.rm = TRUE)

#for(i in 1:nrow(MindfulnessDat)){
#  if(MindfulnessDat$MeanMEIAWeek[i] > 3.56){
#    MindfulnessDat$LevelMEIA[i] <- "high"
#  }
#  else{
#    MindfulnessDat$LevelMEIA[i] <- "low"
#  }
#}
#I'm pretty sure the code above keeps outputing an error, because 2 of the Mean
#MEIA scores output as 'NA'

#after creating the high/low split, an Anova would be done on a linear model
#created from FFMQ scores on the high/low split * before/after split
#lmH3<- lm("put in cleaned variables here")
#Anova(lmH3)
```
